\documentclass[main.tex]{subfiles}
\begin{document}
\section{Obstruction Theory}

Using truncation functors we can define Postnikov towers in any combinatorial
simplicial model category. Recall that a \emph{tower} in \(\mathbf M\) is a
diagram of the form
\[
  \cdots \to X_{n+1}\to X_{n}\to X_{n-1}\to \cdots \to X_{0}
\]
and a \emph{convergent tower} in \(\mathbf M\) is a diagram
\[
  X_{\infty}\xrightarrow{\pi} \cdots \to X_{n+1}\to X_{n}\to\cdots\to X_{0}
\]
exhibiting \(X_{\infty}\) as the homotopy limit of the tower
\({\{X_{n}\}}_{n\in\NN}\), \ie~such that the morphism
\[
  X_{\infty}\xrightarrow{\pi}\holim_{n\in\NN} X_{n}
\]
is a weak equivalence.

\begin{definition}
  Let \(\mathbf M\) be a combinatorial simplicial model category and
  \(X\in\mathbf M\). The tower
  \[
    \cdots\to\trunc{n} X\to\trunc{n-1} X\to\cdots\to\trunc{1} X\to\trunc{0}X
  \]
  is called the \emph{Postnikov tower} for \(X\). The Postnikov tower for \(X\)
  is said to \emph{converge} if
  \[
    X\to\cdots\to\trunc{n} X\to\trunc{n-1} X\to\cdots\to\trunc{1} X\to\trunc{0}X
  \]
  is a convergent tower in \(\mathbf M\).
\end{definition}

\begin{definition}[{cf.~\cite[Definition~7.2.2.20]{mr2522659}}]
  An object \(E\) in a combinatorial simplicial model category \(\mathbf M\)
  which is \((n-1)\)--connected and \(n\)--truncated is an \emph{\(n\)--gerbe}.
  An \(n\)--gerbe in \(\mathbf M/X\) for some \(X\in\mathbf M\) is an
  \emph{\(n\)--gerbe over \(X\)}.

  An \(n\)--gerbe \(E\) equipped with a morphism \(*\to E\) is an
  \emph{Eilenberg--Mac~Lane object in degree \(n\)}.
\end{definition}

\begin{example}
  By definition, the canonical map \(\trunc{n}X \to \trunc{n-1}X\) is an
  \(n\)--gerbe over \(\trunc{n-1}X\).
\end{example}

Given an Eilenberg--Mac~Lane object \(E\) in degree
\(n\),~\autoref{prop:truncated-homotopy-groups}
and~\autoref{prop:connected-homotopy-groups} imply that \(E\) has a single
nontrivial homotopy sheaf \(\pi_n(E)\in\disc(\mathbf M/E)\). If \(n\geq 2\) then
\(\pi_n(E)\) is always equivalent to the pullback of a sheaf of abelian groups
\(A\in\disc(\mathbf M)\)\viktor{Prove this.
  insert~\cite[Lemma~7.2.1.13]{mr2522659} maybe?}. However, this need not be the
case for \(n\leq 1\).

Given a group object \(G\) in a model topos \(\mathbf M\), there always is a
\emph{delooping} \(\Deloop{G}\in\mathbf M\). It can be constructed as follows.
The group object \(G\) determines a simplicial object
\[
  \actgrp{*}{G} = \begin{mytikzcd} \cdots \arrow[r, shift left=2.4ex] \arrow[r,
    shift left=1.2ex] \arrow[r] \arrow[r, shift left=-1.2ex] \arrow[r, shift
    left=-2.4ex] & G\times G\times G \arrow[r, shift left=1.8ex] \arrow[r, shift
    left=.6ex] \arrow[r, shift left=-.6ex] \arrow[r, shift left=-1.8ex] &
    G\times G \arrow[r, shift left=1.2ex] \arrow[r] \arrow[r, shift left=-1.2ex]
    & G \arrow[r, shift left=.6ex] \arrow[r, shift left=-.6ex] & *
  \end{mytikzcd}
\]
and \(\Deloop{G} = \hocolim \actgrp{*}{G}\) is defined to be the homotopy
colimit of this diagram.\viktor{compute loops of this beast, use descent
  statement by Rezk}

\begin{proposition}\label{prop:Deloop-products}
  Let \(\mathbf M\) be a model topos. There is a functor \(F\) from the category
  of group objects in \(\mathbf M\) to \(\mathbf M\) which is compatible with
  products and such that \(F(G)\simeq\Deloop{G}\) for all group objects \(G\) in
  \(\mathbf M\).
\end{proposition}

\begin{proof}
  Choose a presentation for the model topos \(\mathbf M\) as a left exact
  localization
  \[
    \begin{mytikzcd}
      \mathbf M \arrow[r, shift right=.7ex, "i"'] & \arrow[l, shift right=.7ex,
      "L"'] \spshv(\mathbf C).
    \end{mytikzcd}
  \]
  Any such presentation allows one to transfer a functor \(F\) as in the
  proposition from \(\spshv(\mathbf C)\) to \(\mathbf M\). Hence, without loss
  of generality, we can assume \(\mathbf M = \spshv(\mathbf C)\).

  Given a simplicial presheaf of groups in \(\spshv(\mathbf C)\) the
  construction \(\actgrp{*}{G}\) yields a bisimplicial presheaf over \(\mathbf
  C\). Its diagonal \(d(\actgrp{*}{G})\) is weakly equivalent to its homotopy
  colimit\viktor{find a proper reference}, hence \(d(\actgrp{*}{G})\) is a model
  for the Delooping \(\Deloop{G}\) of \(G\). Furthermore, this way of
  constructing \(\Deloop{G}\) is evidently compatible with products\viktor{maybe
    not so evidently?}; as a functor from the category of simplicial presheaves
  of groups on \(\mathbf C\) to \(\spshv(\mathbf C)\).
\end{proof}

An abelian group object \(A\) in \(\mathbf M\) can equivalently be regarded as
an abelian group object in the category of group objects in \(\mathbf M\). Since
product preserving functors send abelian group objects to abelian group objects,
\autoref{prop:Deloop-products} implies that \(\Deloop{A}\) is again an abelian
group object in \(\mathbf M\). It follows that Deloopings \(\Deloop[n]{A}\) of
all orders \(n\in\NN\) exist.

\begin{definition}
  Given a sheaf of abelian groups \(A\in\disc(\mathbf M)\) in a model topos
  \(\mathbf M\) and \(n\in\mathbb N\), the \(n\)--fold Delooping
  \(\Deloop[n]{A}\) of \(A\) is the standard Eilenberg--Mac~Lane object
  \(K(A,n)\).

  Similarly, for a sheaf of groups \(G\in\disc(\mathbf M)\), the Delooping
  \(\Deloop{G}\) is the standard Eilenberg--Mac~Lane object \(K(G,1)\).
\end{definition}

The category \(\mathbf M_*\) of pointed objects \(*\to E\) of \(\mathbf M\)
inherits a simplicial model structure. Given two pointed objects \(E\) and
\(F\), the simplicial set of morphisms from \(E\) to \(F\) in \(\mathbf
M_*\) is given by
\[
  \Hom_{\mathbf M_*}(E,F) = \Hom_{\mathbf M}(E,F) \times_{\Hom_{\mathbf M}(*,
    F)} *;
\]
that is, it is the simplicial set of base point preserving morphisms \(E\to F\).

For \(n\geq 0 \), let \(\EM_n(\mathbf M)\) be the full simplicial subcategory of
\(\mathbf M_*\) on the Eilenberg--Mac~Lane objects of degree \(n\). Let
\(\Cof{\EM_n(\mathbf M)}\) be the full simplicial subcategory of \(\EM_n(\mathbf
M)\) on those object which are fibrant and cofibrant in \(\mathbf M_*\).

Taking sheaves of homotopy groups and pulling back along the base point inclusion defines
simplicial functors
\begin{align*}
  \pi_0\colon&\mathbf M_* \to \disc{(\mathbf M)}_*,\\
  \pi_1\colon&\mathbf M_* \to \grp(\disc(\mathbf M)), \\
  \shortintertext{and}
  \pi_n\colon&\mathbf M_* \to \abgrp(\disc(\mathbf M))\qquad\text{for \(n\geq 2\),}
\end{align*}
where the target categories are considered as simplicial categories with
discrete morphism complexes. For later convenience, we will write
\[G_n(\mathbf M) =
  \begin{cases}
    \disc{(\mathbf M)}_* & \text{for \(n=0\)}\\
    \grp(\disc(\mathbf M)) & \text{for \(n=1\)}\\
    \abgrp(\disc(\mathbf M)) & \text{for \(n\geq 2\),}
  \end{cases}
\]

Our next goal will be to show that the homotopy group functors induce
equivalences of categories \(\pi_n\colon\hoEM_n(\mathbf M)\to G_n(\mathbf M)\)
for all \(n\). Here, \(\hoEM_n(\mathbf M)\) denotes the category with the same
objects as \(\Cof{\EM_n(\mathbf M)}\) but with morphism sets
\[\hom_{\hoEM_n(\mathbf M)}(X, Y) = \pi_0\Hom_{\mathbf M_*}(X,Y),\]
that is, simplicial homotopy classes of base point preserving morphisms in
\(\mathbf M\) between \(X\) and \(Y\).

First, let \(\mathbf M=\sset\) be the category of simplicial sets and
\(\sset_0\) the full subcategory of \emph{reduced} simplicial sets. A simplicial
set \(X\) is called reduced if \(X_0= *\). In~\cite[Section~V]{goerssjardine}
there is a description of a strict model for the \(\infty\)--group structure on the
loop space of a reduced simplicial set. Specifically, denoting by \(\sgrp\) the
category of simplicial groups, there is a functor \(\Gamma\colon
\sset_0\to\sgrp\) such that \(\Gamma(X)\simeq *\times^h_X *\) for all
\(X\in\sset_0\). Additionally, \(\Gamma\) preserves \emph{all} weak
equivalences between reduced simplicial sets;
see~\cite[Proposition~V.6.3]{goerssjardine}. We will need a generalization of
this construction to nonreduced simplicial sets.

To this end, let \(\sgpd\) be the category of simplicially enriched groupoids. A
simplicially enriched functor \(f\colon G\to H\) between \(G,H\in\sgpd\) is a weak
equivalence if it induces a bijection \(\pi_0 G\to \pi_0 H\) on the path components of
\(G\) and \(H\) and for every pair of objects \(x,y\in G\) it induces a weak equivalence
\(\Hom_G(x,y)\to\Hom_H(f(x), f(y))\) of simplicial sets. The category \(\sgpd\)
admits a model structure with these weak equivalences and there is a Quillen equivalence
\[
  \begin{mytikzcd}
    \sgpd \rar[shift right=.7ex][swap]{\wbar} & \lar[shift
    right=.7ex][swap]{\operatorname{G}} \sset,
  \end{mytikzcd}
\]
see~\cite[Section~V.7]{goerssjardine}. In fact,
\cite[Theorem~V.7.8]{goerssjardine} proves the stronger fact that both
\(\operatorname{G}\) and \(\wbar\) preserve all weak equivalences. Let \((X,x)\)
be a pointed simplicial set. It follows from the explicit description of
\(\operatorname{G}(X)\in\sgpd\) in~\cite[Section~V.7]{goerssjardine} that the set
of objects of \(\operatorname{G}(X)\) coincides with the set \(X_0\) of
\(0\)--simplices of \(X\). In particular, \(x\in \operatorname{G}(X)\) and we
have the full simplicially enriched subgroupoid \(\operatorname{G}(X)(x,x)\) of
\(\operatorname{G}(X)\) on the single object \(x\). The explicit description of
the functor \({\wbar}\) then shows that the simplicial set
\(\wbar(\operatorname{G}(X)(x,x))\) is reduced with unique \(0\)--simplex \(x\).
Consequently, we can apply Kan's loop group functor \(\Gamma\colon \sset_0\to\sgrp\) and
obtain a simplicial group \(\kanloop{X} \coloneqq \Gamma\wbar(\operatorname{G}(X)(x,x))\).

\begin{lemma}
  The construction \(\kanloop{X}\) defines a functor \(\sset_*\to\sgrp\) from
  pointed simplicial sets to simplicial groups. This functor preserves all pointed weak
  equivalences between pointed and connected simplicial sets and for each pointed and
  connected simplicial set \((X,x)\) there is a weak equivalence \(\kanloop{X} \simeq
  \{x\}\times^h_{X}\{x\}\) which is natural up to homotopy in \(X\).
\end{lemma}
\begin{proof}
  The functoriality of \(\kanloop{}\) is clear. Let \((H, h)\) be a pointed and
  connected simplicially enriched groupoid and write \(H(h,h)\) for the full
  simplicially enriched subgroupoid of \(H\) on the single object \(h\).
  Then the inclusion \(H(h,h)\into H\) is a weak equivalence of simplicially
  enriched groupoids because \(H\) is connected. Because \(\wbar\) preserves weak
  equivalences between all simplicial groupoids the map \(\wbar H(h,h)\to \wbar
  H\) induced by the inclusion is a weak equivalence as well.

  For \((X,x)\) a pointed and connected simplicial
  set,~\cite[Theorem~V.7.8]{goerssjardine} implies that the adjunction unit \(X
  \to \wbar \operatorname{G}(X)\) is a weak equivalence. Because \((\operatorname
  G(X), x)\) is a pointed and connected simplicially enriched groupoid we
  therefore have a zig-zag of weak equivalences
  \[
    X \to \wbar\operatorname{G}(X) \from \wbar(\operatorname{G}(X)(x,x))
  \]
  and so we conclude that \(\{x\}\times^h_X\{x\}\simeq
  \{x\}\times^h_{\wbar(\operatorname{G}(X)(x,x))}\{x\}\). But now the simplicial set
  \(\wbar(\operatorname{G}(X)(x,x))\) is reduced and
  so~\cite[Corollary~V.5.11]{goerssjardine} applies to show that
  \[\kanloop{X} =
    \Gamma\wbar(\operatorname{G}(X)(x,x))\simeq
    \{x\}\times^h_{\wbar(\operatorname{G}(X)(x,x))}\{x\}\simeq\{x\}\times^h_X\{x\}.\]

  If \((Y,y)\) is another pointed and connected simplicial set with a pointed
  weak equivalence \(X\to Y\), then we have a commutative diagram
  \[
    \begin{tikzcd}
      X \dar \rar & \wbar\operatorname{G}(X)\dar & \lar \dar\wbar(\operatorname{G}(X)(x,x)) \\
      Y \rar & \wbar\operatorname{G}(Y) & \lar\wbar(\operatorname{G}(Y)(y,y))
    \end{tikzcd}
  \]
  of simplicial sets. All horizontal and the two leftmost vertical maps are weak
  equivalences because both \(\wbar\) and \(\operatorname{G}\) preserve all weak
  equivalences. It follows that the rightmost map is a weak equivalence as well
  and because \(\Gamma\) preserves all weak equivalences we conclude that
  \(\kanloop{X}\to\kanloop{Y}\) is a weak equivalence.
\end{proof}

\begin{lemma}\label{lem:Gn-equivalence}
  For all \(n \geq 1\), there is an equivalence \(G_n(\mathbf M) \simeq \grp(G_{n-1}(\mathbf M))\) of
  categories, hence also of (discrete) simplicial categories.
\end{lemma}
\begin{proof}
  For the case \(n=1\) we just need to observe that group objects in
  \(\disc(\mathbf M)_*\) coincide with group objects in \(\disc(\mathbf
  M)\).\viktor{Why is that true?} The case \(n>1\) is the Eckmann--Hilton
  argument.
\end{psoof}

\begin{lemma}
  For each \(n\geq 1\), the functor \(\pi_n\colon\EM_n(\mathbf M) \to G_n(\mathbf M)\)
  factors as
  \[
    \begin{mytikzcd}
      \EM_n(\mathbf M) \rar{\pi_n} \dar[swap]{\kanloop{}} & G_n(\mathbf M) \\
      \grp(\EM_{n-1}(\mathbf M)) \rar[swap]{\pi_{n-1}} & \grp(G_{n-1}(\mathbf M))
      \uar[swap]{\simeq}
    \end{mytikzcd}
  \]
  up to natural isomorphism.
\end{lemma}
\begin{proof}
  Because the homotopy group functor \(\pi_{n-1}\) preserves products, it induces a functor \(\grp(\EM_{n-1}(\mathbf M)) \to \grp(G_{n-1}(\mathbf M))\) on group objects. Using \autoref{lem:Gn-equivalence}, we only need to see that \(\pi_{n-1}(\kanloop{X}) \isom \pi_n(X)\) naturally in \(X\in\EM_n(\mathbf M)\). From [previous result\viktor{Fill in the details}] we have a weak equivalence \(\kanloop{X}\simeq \{*\}\times^h_X\{*\}\) which is natural up to homotopy in \(X\). This gives in particular the required natural isomorphism \(\pi_{n-1}(\kanloop{X})\isom\pi_n(X)\).
\end{proof}

\begin{proposition}\label{prop:uniqueness-em-objects}
  Let \(E\) be a degree \(n\) Eilenberg--Mac~Lane object in a model topos
  \(\mathbf M\). Assume that there is a sheaf of groups \(G\in\disc(\mathbf M)\)
  such that \(\pi_n(E)\isom E\times G\). Then there is a base point preserving
  equivalence \(E\to K(G,n)\).
\end{proposition}
\begin{proof}
  For \(n=0\) this is trivial. Let \(n\geq 1\) and assume \(E\) is a degree
  \(n\) Eilenberg--Mac~Lane object with base point \(e\colon *\to E\). By the
  factorization lemma of~\cite{MR0341469} there is a factorization \(e = p\circ
  i\) with \(p\colon P\to E\) a fibration and \(i\colon *\to P\) right inverse
  to an acyclic fibration \(r\colon P\to *\).
\end{proof}
\begin{remark}
  The assumption that \(\pi_n(E)\) be a pullback in
  \autoref{prop:uniqueness-em-objects} is automatic for \(n\geq
  2\).\viktor{reference connectedness statements}
\end{remark}

\begin{proposition}\label{prop:gerbe-classification}
  Assume \(E\) is an \(n\)--gerbe in a model topos \(\mathbf M\). Then \(E\times
  E\) equipped with the diagonal \(E\to E\times E\) is a degree \(n\)
  Eilenberg--Mac~Lane object in \(\mathbf M/E\). If additionally \(\pi_n(E)
  \simeq f^*G\) for \(f\colon E\to *\) and some sheaf of groups
  \(G\in\disc(\mathbf M)\), then there is a morphism \(g\colon * \to K(G,n)\)
  whose homotopy fiber is equivalent to \(E\).
\end{proposition}
\begin{proof}
  \viktor{write proof}
\end{proof}

\begin{theorem}
  Given a map \(f\colon Y\to \trunc{n}X\), there exists a lift \(g\colon
  Y\to\trunc{n+1}X\) making the diagram
  \[
    \begin{mytikzcd}
      & \trunc{n+1} X \arrow[d] \\
      Y \arrow[r, "f"'] \arrow[ru, "g"] & \trunc{n} X
    \end{mytikzcd}
  \]
  commute up to homotopy if and only if the associated class in \(H^{n+2}(Y,
  \pi_{n+1}X)\) vanishes.
\end{theorem}
\end{document}

% Local Variables:
% tex-main-file: "main.tex"
% End:
